Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
improve input data
describe the size of the data to be handled. #13

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{amsmath}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{lccc} 
    \toprule
    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
    gis.json & 23 M & 117M & 470 M \\
    mesh\_lod0.msh & 17 M & 112M & 496 M \\
    mesh\_lod1.msh & 44 M & 240M & 896 M \\
    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
    \bottomrule
  \end{tabular}
\end{center}
\caption{Size comparison of input data using New York city.}
\label{tab:input-data-size-comparison}
\end{table}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{amsmath}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

@@

\begin{table}[ht]
  \centering
  \caption{Size comparison of input data files for different geographical extents in New York City}
  \label{tab:input-data-size-comparison}
  \begin{tabularx}{.8\linewidth}{l *{3}{>{\RaggedLeft\arraybackslash}X}} 
      \toprule
      \textbf{Files} & \textbf{\text{4 $\times$ 4} \si{\kilo\meter\squared}} & \textbf{\text{10 $\times$ 10} \si{\kilo\meter\squared}} & \textbf{\text{20 $\times$ 20} \si{\kilo\meter\squared}} \\
      \midrule
      \texttt{geographicdata\_setup.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\ 
      \texttt{gis.json} & \SI{23}{\mega\byte} & \SI{117}{\mega\byte} & \SI{470}{\mega\byte} \\
      \texttt{mesh\_lod0.msh} & \SI{17}{\mega\byte} & \SI{112}{\mega\byte} & \SI{496}{\mega\byte} \\
      \texttt{mesh\_lod1.msh} & \SI{44}{\mega\byte} & \SI{240}{\mega\byte} & \SI{896}{\mega\byte} \\
      \texttt{weather-data-0.hourly-variables.csv} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} \\
      \texttt{weather-data.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\
      \bottomrule
  \end{tabularx}
  \end{table}

In the future, the input data is expected to grow even larger with the addition of new details such as roofs, building characteristics, vegetation (e.g., trees), and terrain information.
These enhancements will increase the complexity and accuracy of the simulation and the amount of data required to accurately model the urban environment.
